---
title: "Title here"
author: |
  | Corresponding author: 
  | Joseph V. Casillas (joseph.casillas@rutgers.edu)
  |
  | Contributing authors: 
  | Kyle Parrish, Juan José Garrido Pozú, Laura Fernández Arroyo, 
  | Gabriela Constantin-Dureci, Jiawei Shao, Iván Andreu Rascón, 
  | Isabelle Chang, Katherine Taveras, Melany Subina
header-includes:
  - \usepackage{setspace}
  - \doublespacing
indent: true
csl: "../lit/apa-6th-edition.csl"
bibliography: "../lit/speech_in_noise.bib"
output: pdf_document
---

```{r, eval=F, echo=F}
# Study to be replicated and justification. The study to be replicated should have had an impact on subsequent empirical and/or theoretical work in the field of SLA. A justification should be provided for why the study has been selected for replication.

# Type of replication. The proposal should describe and motivate the approach to replication (exact, close, approximate, conceptual [Porte & McManus, 2019]). While all approaches to replication will be considered, preference will be given to close or approximate replication studies in which one or maximally two major variables have been modified.

# Variable modification. The variable(s) selected for modification should be described and a rationale should be provided for why the variables were selected and how they will be modified.

# Design and availability of materials. The design of the replication study should be described so that all major aspects of the methodology can be evaluated, including availability of the initial study’s materials.

# Analysis. The proposal should describe how the data will be analyzed and to what extent the procedures for data preparation and analysis are similar/different from the initial study.

# Other differences (if relevant). All differences with the initial study should be identified. In order to communicate similarities and differences between the initial study and the replication, authors are recommended to use Brandt et al.’s (2014) Replication Recipe as a guide (available from: https://osf.io/4jd46/).

# Impact. Authors should make clear how the proposed replication has the potential to advance knowledge and understanding in the field of SLA.

# library("trackdown")
# library("here")

# upload_file(here("docs", "proposal", "README.Rmd"))
# update_file(here("docs", "proposal", "README.Rmd"))
# download_file(here("docs", "proposal", "README.Rmd"))
# render_file(here("docs", "proposal", "README.Rmd"))
```

```{r, power, echo=F, message=F, warning=F}
library("tidyverse")
library("esc")
library("pwr")

# Hardest condition
# Bi: mean = 11.43, se = 0.795, n = 12
# Mono: mean = 15.40, se = 0.815, n = 15

effect_hard <- esc_mean_se(
  study = "Rogers et al. (2006)", 
  grp1m = 11.43, grp1se = 0.795, grp1n = 12, 
  grp2m = 15.40, grp2se = 0.815, grp2n = 15, 
  es.type = "d") |> 
   unlist() |>
   as.list() |> 
   tibble::as_tibble() |> 
   mutate(es = as.numeric(es), 
     ci.lo = as.numeric(ci.lo), ci.hi = as.numeric(ci.hi)) %>% 
   mutate_if(is.numeric, round, digits = 2) 

# Second hardest
# Bi: mean = 15.91, se = 0.495, n = 12
# Mono: mean = 18.37, se = 0.595, n = 15

effect_med <- esc_mean_se(
  study = "Rogers et al. (2006)", 
  grp1m = 15.91, grp1se = 0.495, grp1n = 12, 
  grp2m = 18.37, grp2se = 0.595, grp2n = 15, 
  es.type = "d") #|> 
  # unlist() |>
  # as.list() |> 
  # tibble::as_tibble()

# Easiest
# Bi: mean = 18.21, se = 0.5, n = 12
# Mono: mean = 19.88, se = 0.535, n = 15

effect_easy <- esc_mean_se(
  study = "Rogers et al. (2006)", 
  grp1m = 18.21, grp1se = 0.5, grp1n = 12, 
  grp2m = 19.88, grp2se = 0.535, grp2n = 15, 
  es.type = "d") #|> 
  # unlist() |>
  # as.list() |> 
  # tibble::as_tibble()

# Large effect size
large80p <- pwr.t.test(
  sig.level = 0.05, 
  d = -1.38,
  power = 0.8, 
  type = "two.sample",
  alternative = "two.sided") 

# Large effect size (upper bound)
large80p_2 <- pwr.t.test(
  sig.level = 0.05, 
  d = -0.54,
  power = 0.8, 
  type = "two.sample",
  alternative = "two.sided") 

# Medium effect size
medium80p <- pwr.t.test(
  sig.level = 0.05, 
  d = -1.236,
  power = 0.8, 
  type = "two.sample",
  alternative = "two.sided") 

# Small effect size
small80p <- pwr.t.test(
  sig.level = 0.05, 
  d = -0.898,
  power = 0.8, 
  type = "two.sample",
  alternative = "two.sided") 

```

# Study to be replicated and justification

Adverse listening conditions, such as a noisy room, can make understanding speech difficult. 
This occurs because less intense regions of the speech signal can be masked and rendered unintelligible by extraneous noise in the acoustic environment [@helfer_1990]. 
As a result, speech perception in noise is more difficult due to decreased acoustic and linguistic cues available to the listener and becomes increasingly more difficult as the signal to noise ratio (SNR) decreases. 
This is particularly true when listening in one's non-native language (referred to in the literature as the 'native advantage'). 
Three decades of research on speech perception in adverse conditions consistently shows that listening in background noise poses more difficulties for bilinguals listening in their L2 than for monolinguals [See @scharenborg2019listening for an overview]. 
Furthermore, some studies show that the ‘native advantage’ persists even when one is highly proficient in the L2 and learns it at an early age [See @mayo_1997; @meador_flege_mackay_2000; @rogers_etal_2006, among others], including simultaneous bilinguals with two L1’s [@mayo_1997; @shi_2010]. 

According to @scharenborg2019listening, the ‘native advantage’ results from 'imperfect knowledge' of the L2. 
This explanation seems plausible for late learners, but cannot explain the apparent difficulties of early sequential and simultaneous bilinguals that are proficient in both languages. 
A recent study by @reetzke_2016 finds that simultaneous bilingual children exhibit comparable difficulties perceiving speech in noise as age-matched monolingual peers. 
Thus, contrary to initial findings, the ‘native advantage’ cited in the literature may also include individuals with multiple native languages. 

What, then, can explain the simultaneous and early bilinguals’ difficulties cited in the early studies? 
One possibility is type-I error. 
In other words, the early studies on bilingual speech perception in noise may present false-positive results. 
Type-I errors are common in studies with low power; studies with small sample sizes are virtually always underpowered. 
The investigations in question include samples ranging from 3 to 18 participants per group. 
We believe that the current assessment of the ‘native advantage’ is incomplete with regard to simultaneous and early bilingual adults. 
Thus, the question we intend to address with our replication is the following: Do simultaneous and early sequential bilingual adults have more difficulty perceiving speech in noise than monolinguals?
We propose a multi-site replication of @reetzke_2016.

# Type of replication

We will complete a close replication of the @reetzke_2016 study, with several minor differences. 
The theoretical/conceptual framework is the same. 
Our research questions/hypotheses also parallel those of @reetzke_2016, with slight differences due to the population of interest.
The research design is the same, as are the procedures we will use for presenting stimuli and coding the listening task. 
We will use the same stimuli, if possible, or recreate them using similar equipment. 
The participants’ profile is slightly different with regard to the @reetzke_2016 study. 
Specifically, we are interested in adult bilinguals, both simultaneous and early sequential.
We will also employ most of the same analytic strategies, though we use a Bayesian framework. 
The primary differences from our study and that of @reetzke_2016 deal with the population of interest and the modality of the stimuli, which we describe in the following section. 

# Variable modification

With regard to variable modification, our study will differ from that of @reetzke_2016 in two ways. 
First, we will recruit a participant sample of adult Spanish-English bilinguals, as opposed to Spanish-English simultaneous bilingual children. 
The rationale for expanding the participant pool to adults is straightforward. 
We want to test the ‘native advantage’ attested in the literature with a comparable population (adults) and an adequate sample size. 
Thus far, the only studies showing a monolingual advantage with regard to simultaneous/early bilinguals have included small samples of adults. 
Thus, we believe this decision more closely aligns our study with the previous investigations, which have focused on bilinguals at or near the end state of their language development [e.g., @mayo_1997; @meador_flege_mackay_2000; @rogers_etal_2006, among others]. 
In the same vein, we will extend the findings from @reetzke_2016 to include early sequential bilinguals. 
In line with the previous research, we operationalize early bilinguals as individuals that have been exposed to their L2 at or before the age of 6. 
Importantly, we will still include simultaneous bilinguals as part of our sample. 
Second, we will omit one of the conditions used in @reetzke_2016, the audio-visual condition. 
Previous research on speech perception in noise finds that listening when audio and visual information are both available results in higher accuracy than when only auditory information is presented. 
Our study is concerned with speech perception in noise in the most difficult listening conditions, thus we believe this condition would be redundant in our study. 

In sum, our replication of @reetzke_2016 includes two subtle modifications. 
Our “group” factor focuses on adults and includes three levels rather than two (monolingual control, simultaneous bilingual, early sequential bilingual) and we do not include a “modality” factor (only auditory stimuli). 

# Design and availability of materials

The original materials from @reetzke_2016 are not publically available. 
We are in contact with the corresponding author in order to obtain the original materials. 
At the time of writing this proposal, the corresponding author is looking for the sound files. 
In the case that we are not able to obtain the original materials, we will recreate them using professional recording equipment. 
The process of recreating the stimuli is well-documented in the manuscript and appears to be straightforward. 

# Analysis

## Statistical analyses

Our primary analysis will mirror that of the original study.
Specifically, the outcome variable of @reetzke_2016 was the number of correct responses from a speech perception in noise task. 
Participants heard Basic English Lexicon (BEL) sentences (e.g., “The hot sun warmed the ground”) with two masker types (2-speaker babble and pink noise) at SNRs of -16, -12, -8, -4, -2,  and 0. 
The data were analyzed using mixed effects logistic regression models (correct responses coded as ‘1’) with masker-type and signal to noise ratio as fixed effects (signal to noise was a continuous variable). 
We will use the same analytic strategy as @reetzke_2016 under a Bayesian framework. 

## Sample size

The @reetzke_2016 study included two groups of participants, monolinguals (n = 12) and simultaneous bilinguals (n = 12). 
This sample size parallels those of the most closely related investigations [@mayo_1997; @meador_flege_mackay_2000; @rogers_etal_2006]. 
In order to approximate the minimum sample size for our study, we estimated the effect size from the @rogers_etal_2006 study in the most difficult listening condition (SNR = -6).
This study was selected because the analytic strategy more closely resembles that of @reetzke_2016. 
We calculated Cohen’s D to be `r abs(effect_hard$es)` (CI: `r abs(effect_hard$ci.hi)`, `r abs(effect_hard$ci.lo)`).
Given the wide CI, we used the lower-bound of this estimate to approximate a conservative sample size of approximately `r round(large80p_2$n)` participants per group at 80% power. 

# Other differences

Our intention is that this replication be a lage(r) scale, multi-site replication, including research teams from across the United States. 
Each team would collect data independently, following the same procedures detailed in a forthcoming pre-registration. 
The aforementioned statistical analysis would include the pooled sample from all labs. 
Additionally, we will investigate the ‘native advantage’ effect using Bayesian meta-analytic techniques.
The corresponding author of the present proposal has previous experience managing multi-site collaborations (see https://many-speech-analyses.github.io for an example). 
At this time, three additional research teams have expressed interest in participating. 

# Impact

The general claim resulting from the speech perception in noise research is that bilingual individuals, in comparison with monolinguals, have more difficulties with speech perception when the acoustic environment includes extraneous noise, which, in our estimation, is nearly all the time. 
The extant literature sheds doubt on this claim, particularly regarding simultaneous and early sequential bilinguals. 
Thus, currently there is a discourse supporting a bilingual disadvantage that may not be warranted. 
We believe that a large-scale replication of @reetzke_2016 can shed light on the topic, furthering our knowledge of both bilingualism and speech perception in noise. 

\clearpage

# References
